### 2022-03-22 ms/PrestigeBias.tex
update

\section{Abstract}
Copying our role-models have always been an efficient method of acquiring knowledge. Copying successful role-model is one of the methods of cultural transmission of traits. In this paper, we study the various biases and their effects of the population and it's evolution. The most common bias when choosing a role-model to copy is \textit{success bias}, i.e copying whoever appears successful to us. This estimation is based on the performance of the role-model alone, without any other factors. Here, we study another factor we believe aids to better model the cultural inheritance of traits in a large population. \textit{Influence bias} is a bias evaluated by the number of copiers a role-model already has. In our model we combine these components to what we call the \textbf{Prestige bias} and analyze its relationship to the dynamics of the population. We successfully found mathematical approximations to our model, easing the mathematical analysis and the computation power required for simulations. We show the value of these approximations using simulations, and their robustness to variations such as mutation and other relaxations required for the mathematical proofs.
In the binary form of our model, we found alternatives to \textit{Kimura's} equations for approximating fixation probability and time to fixation of an invading advantageous trait, in both a constant and changing environment. We show that \textit{Influence} solely affects the effective population size.
We found that influence acts as an accelerator for a state of the population, matching the \textit{rich getting richer} it was based on.
We believe such model better describes how humans acquire knowledge from one another, mainly in the last years where social networks are very popular. Social networks allow easy access to estimate number of copiers a role-model has, with little to no effort.

@@

%prestige bias - what is it, what's missing
Prestige means having a good reputation or high-esteem, therefore does not directly signify success (although it may imply it), making it an \textit{indirect bias}.
Both \citet[Ch. 8]{evolutionBook} and \citet{complexityPaper} claim that prestige biases are probably more common in humans than success biases.
\citet[Ch. 8]{evolutionBook} add that maladaptive traits may spread widely in a population, if the indirect bias is strong enough.
They claim the bias could lead to a \textit{runaway process}, caused by a cultural equivalent of \textit{sexual selection} \citep{sexualSelectionBook}.
On the other hand, \citet{henrichBroesch} claim that prestige biases, over generations, can lead to cultural adaptations.
According to them, prestige can make a maladaptive trait spread in the population, but can also accelerate the spread of adaptive traits as well.
\textit{Prestige bias} is often mentioned in the literature, but seldom modeled.
\citet{evolutionBook} have modeled the prestige bias, but didn't include the effects the copiers of a role-model has on the probability of other individuals to choose the same role model.\\
This effect is similar to \textit{conformity} \citep{conformity}, which is usually modeled as a different bias.
\textit{Conformist learning} (imitating locally common behaviors) is a known bias in cultural transmission \citep{conformism}, and we suggest that prestige bias is made up by both indirect bias and a new type of conformity.
Our new component, \textit{influence}, is assigned to a role-model, contrary to conformity, which refers to the frequency of a trait in the population, regardless which individuals posses it.
\textbf{The goal of this study is to define a more realistic model for prestige bias and analyze the dynamics of the population it causes}.

>>>>

\section{Abstract}
Copying our role-models have always been an efficient method of acquiring knowledge \citep{strategiesPaper}. \textbf{In this paper, we study the effects of prestige as a cultural transmission bias} on the population. A common bias when choosing a role-model to copy is \textit{success bias}, i.e copying whoever appears successful to us \citep{evolution_of_cultural_evolution}. This estimation is based on the performance of the role-model alone, without any other factors. We propose an additional factor we believe aids to better model the cultural inheritance of traits in a large population. \textit{Influence bias} is a bias evaluated by the number of copiers a role-model already has \citep{prestige_evolution}.We combine these components to what we call the \textit{prestige bias} and analyze its effects on the dynamics of the population. \textbf{We present a model of prestige bias} as we defined it, and \textbf{observe the dynamics of the population using computer simulations}. We also \textbf{analyze our model using mathematical approximations}. We successfully found mathematical approximations to our model, easing the mathematical analysis and the computation power required for simulations. We show the value of these approximations using simulations, and their robustness to variations such as mutation and other relaxations required for the mathematical proofs.
In the binary form of our model, we found alternatives to \textit{Kimura's} equations for approximating fixation probability and time to fixation of an invading advantageous trait, in both a constant and changing environment. We show that \textit{Influence} solely affects the effective population size.
We found that influence acts as an accelerator for a state of the population, matching the \textit{rich getting richer} it was based on.
\textbf{We believe such model better describes how humans acquire knowledge from one another, mainly in the last years where social networks are very popular}.
Furthermore, we believe that our model could predict various phenomena in human culture once supplemented with more natural concepts like natural selection and costs.

@@

%prestige bias - what is it, what's missing
Prestige means having a good reputation or high-esteem, therefore does not directly signify success (although it may imply it), making it an \textit{indirect bias}.
Both \citet[Ch. 8]{evolutionBook} and \citet{complexityPaper} claim that prestige biases are probably more common in humans than success biases.
\citet[Ch. 8]{evolutionBook} add that maladaptive traits may spread widely in a population, if the indirect bias is strong enough.
They claim the bias could lead to a \textit{runaway process}, caused by a cultural equivalent of \textit{sexual selection} \citep{sexualSelectionBook}.
On the other hand, \citet{fijian_social_bias} claim that prestige biases, over generations, can lead to cultural adaptations.
According to them, prestige can make a maladaptive trait spread in the population, but can also accelerate the spread of adaptive traits as well.
\textit{Prestige bias} is often mentioned in the literature, but seldom modeled.
\citet{evolutionBook} have modeled the prestige bias, but didn't include the effects the copiers of a role-model has on the probability of other individuals to choose the same role model.\\
This effect is similar to \textit{conformity} \citep{conformity}, which is usually modeled as a different bias.
\textit{Conformist learning} (imitating locally common behaviors) is a known bias in cultural transmission \citep{conformism}, and we suggest that prestige bias is made up by both indirect bias and a new type of conformity.
Our new component, \textit{influence}, is assigned to a role-model, contrary to conformity, which refers to the frequency of a trait in the population, regardless which individuals posses it.
\textbf{The goal of this study is to define a more realistic model for prestige bias and analyze the dynamics of the population it causes}.
